Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-04-06 paper/paper.qmd
Paper structure updated

The structure of this paper is as follows. @sec-method outlines our data and methodology. Section 3 presents our quantitative analysis. In Section 4, we discuss the results and address our findings

@@

# Plots

@@

# Analysis

@@

# Discussion

@@

# Limitations

@@

# Conclusion

@@

# References

>>>>

The structure of this paper is as follows. @sec-method outlines our data and methodology. @sec-plots presents our findings into graphs and charts to visualize the data better. @sec-analysis presents our quantitative analysis. In @sec-disc, we discuss the results and address our findings. We end off, we have the limitations and conclusion in @sec-lims and @sec-conc, respectively.
All of the code used for this study can be found in @sec-appendix. The references are found in @sec-references.

@@

# Plots {#sec-plots}

@@

# Analysis {#sec-analysis}

@@

# Discussion {#sec-disc}

@@

# Limitations {#sec-lims}

@@

# Conclusion {#sec-conc}

@@

# References {#sec-references}
